Performance benefits of Intel Optane DC storage for the parallel processing of large neuroimaging data

### 2019-10-22 paper.tex
normalized colours in figures

\subsection{40~$\mu$m \bigbrain incrementation}
\subsubsection{25 Processes}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-25cpus-120delay-1it.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Makespan of \bigbrain Incrementation using 25 processes with a sleep delay of 120s on 125 blocks on the 40~$\mu$m image given different storage configurations. 5 repetitions were performed.}\label{fig:makespan-25cpus}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/stacked-25cpus-120delay-1it.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Total read/increment/write breakdown of \bigbrain Incrementation using 25 processes with a sleep delay of 120s on 125 blocks on the 40~$\mu$m image given different storage configurations. 5 repetitions were performed.}\label{fig:stacked-25cpus}
\end{figure}
\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567709282-tmpfsAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{tmpfs}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567705458-optaneAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Optane}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567704324-localAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{local disk}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567707833-isilonAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Isilon}\label{fig:gantt25isilon}
\end{subfigure}
\caption{Gantt charts for each storage device (App Direct Mode) processing 125 blocks of the 40$\mu$m BigBrain using 25 processes and a sleep delay of 120s}\label{fig:gantt25}
\end{figure*}

@@

The read/increment/write breakdown (Figure~\ref{fig:20stackedp25}) shows that tmpfs
spends the least amount of time executing all the tasks, however, it spends more
time than Optane incrementing the data. Otherwise, tmpfs is nearly 470x faster with
reading and nearly 11x faster at writing than Optane. Despite not reaching memory
speeds, Optane is significantly faster than other persistent storage devices.

\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-real-20bb_25cpus.pdf}
    \caption{real}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-em-20bb_25cpus.pdf}
    \caption{emulated}
\end{subfigure}
\caption{Makespan of the incrementation algorithm processing the 20~$\mu$m BigBrain using
25 processes}\label{fig:20mksp25}
\end{figure*}

@@

\subsubsection{96 Processes}
\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-real-20bb_96cpus.pdf}
    \caption{real}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-em-20bb_96cpus.pdf}
    \caption{emulated}
\end{subfigure}
\caption{Makespan of the incrementation algorithm processing the 20~$\mu$m BigBrain using
96 processes}\label{fig:20mksp96}
\end{figure*}

>>>>

\subsection{40~$\mu$m \bigbrain incrementation}
\subsubsection{25 Processes}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-real-25cpus-120delay-1it.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Makespan of \bigbrain Incrementation using 25 processes with a sleep delay of 120s on 125 blocks on the 40~$\mu$m image given different storage configurations. 5 repetitions were performed.}\label{fig:makespan-25cpus}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/stacked-real-25cpus-120delay-1it.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Total read/increment/write breakdown of \bigbrain Incrementation using 25 processes with a sleep delay of 120s on 125 blocks on the 40~$\mu$m image given different storage configurations. 5 repetitions were performed.}\label{fig:stacked-25cpus}
\end{figure}
\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567709282-tmpfsAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{tmpfs}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567705458-optaneAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Optane}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567704324-localAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{local disk}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567707833-isilonAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Isilon}\label{fig:gantt25isilon}
\end{subfigure}
\caption{Gantt charts for each storage device (App Direct Mode) processing 125 blocks of the 40$\mu$m BigBrain using 25 processes and a sleep delay of 120s}\label{fig:gantt25}
\end{figure*}

@@

The read/increment/write breakdown (Figure~\ref{fig:20stackedp25}) shows that tmpfs
spends the least amount of time executing all the tasks, however, it spends more
time than Optane incrementing the data. Otherwise, tmpfs is nearly 470x faster with
reading and nearly 11x faster at writing than Optane. Despite not reaching memory
speeds, Optane is significantly faster than other persistent storage devices.
For instance, it can be almost up to 10x faster in reads than Isilon and almost 
9x faster in writes. It is important, however, to note that total read times in App
Direct mode for the Spark execution on Isilon are almost twice as fast as their 
equivalent Optane counterpart. On the other hand, this decrease read time is offset
by the write time which are 9x slower.

Emulated breakdown results also agree that the bulk of the differences in makespans
can be attributed to write time, with local disk writes being notably slower than
Optane. In fact, local disk write speeds nearly match that of Isilon. Isilon results
in a longer makespan due to increase read and incrementation time.
\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-real-20bb_25cpus.pdf}
    \caption{real}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-em-20bb_25cpus.pdf}
    \caption{emulated}
\end{subfigure}
\caption{Makespan of the incrementation algorithm processing the 20~$\mu$m BigBrain using
25 processes}\label{fig:20mksp25}
\end{figure*}

@@

\subsubsection{96 Processes}

With nearly a four-fold increase in parallelization, the makespan generally did
not improve other but a few 100s on Isilon. Overall, the general trend is similar
than with 25 cpus. As can be seen in Figure~\ref{fig:20mksp96}, tmpfs is the
fastest storage device. Regardless, Optane remains significantly faster than the
other storage devices (e.g. Isilon). However, emulated disk results appear to 
imply that the speedup difference between Optane and local disk will be smaller.

\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-real-20bb_96cpus.pdf}
    \caption{real}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-em-20bb_96cpus.pdf}
    \caption{emulated}
\end{subfigure}
\caption{Makespan of the incrementation algorithm processing the 20~$\mu$m BigBrain using
96 processes}\label{fig:20mksp96}
\end{figure*}
